---
title: "Financial modeling and Analysis"
editor: visual
---

This chapter explains the principles of financial modeling and analysis for energy projects, including cash flow analysis, discounted cash flow (DCF) analysis, sensitivity analysis, and financial metrics (e.g., NPV, IRR).

We use `dplyr` for data manipulation and `ggplot2` for visualization.

```{r, message=FALSE}
library(dplyr)
library(ggplot2)
```

First, we read in data for cash flow of a hypothetical energy business.

```{r}
# Load the cash flow data
cash_flow_data <- read.csv("cashflow_energy.csv")
```

```{r}
head(cash_flow_data)
```
The data includes: revenue, operating expenses, capital expenditures, and working capital.

We calculate cash flow by substracting all other variables from revenue. Revenue is what we are getting and others are expenses.

```{r}
cash_flow_data <- cash_flow_data %>%
  mutate(CashFlow = Revenue - OperatingExpenses - CapitalExpenditures - WorkingCapital)
```

We plot the cash flow every year.

```{r}
ggplot(cash_flow_data, aes(x = Year, y = CashFlow)) +
  geom_line() +
  labs(x = "Year", y = "Cash Flow", title = "Cash Flow Analysis") +
  theme_minimal()
```
Cumulative cashflow and visualization

```{r}
cash_flow_data <- cash_flow_data %>%
  mutate(CumulativeCashFlow = cumsum(CashFlow))
```

```{r}
ggplot(cash_flow_data, aes(x = Year, y = CumulativeCashFlow)) +
  geom_line() +
  labs(x = "Year", y = "Cumulative Cash Flow", title = "Cumulative Cash Flow Analysis") +
  theme_minimal()
```
Net Present Value

```{r}
discount_rate <- 0.10

npv <- sum(cash_flow_data$CashFlow / (1 + discount_rate)^(cash_flow_data$Year - min(cash_flow_data$Year)))
```

```{r}
cat("Cash Flow Analysis Results:\n")
print(cash_flow_data)
```


```{r}
cat("\nNet Present Value (NPV):\n")
print(npv)
```

